Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2014-02-23 BackMatter/paper.tex
core-shell paper

\ce{MoOx} few layer as hole selective contact in solar cell.\cite{Battaglia2014}
\ce{MoO_x} on n-type Si acts as a high workfunction metal (6.6eV), enabling a dopant-free contact and thus junctionless devices.

@@

\section{TMS}
\cite{Cong2013} A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.

@@

ref M. Cardona. Light Scattering in Solids II,. Springer, Berlin, 1982

@@

@@

in reciprocal space, primitive cell, a sketch of device, a decisive role. anchors,

>>>>

\ce{MoOx} few layer as hole selective contact in solar cell.\cite{Battaglia2014}
\ce{MoO_x} on n-type Si acts as a high work function metal (6.6eV), enabling a dopant-free contact and thus junctionless devices.

@@

\section{TMS}

\cite{Najmaei2014} Self-assembled monolayer (SAM) on \ce{SiO2} and its effect on \ce{MoS2} 1L.

\cite{Ma2011} \ce{WS2} 1L doping calculation.

\cite{Britnell2013} G/\ce{WS2}/G stacked solar cell. For lubricant, and surface protection. Absorption $\sim 10^7 m^{-1}$.

\cite{Cong2013} A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.

@@

@@

Light Scattering in Solids II,. Springer, Berlin, 1982

influence of core WOx, Raman scattering by plasma-LO coupling to determine carrier concentration. measure resonant cross sections in absolute units.

disorder-induced light scattering, Van Hove critical points,
In resonant second-order scattering:
overtone: the same phonon,
combination: two different phonons;

\[
\frac{\ud\sigma}{\ud\Omega}= \omega_s^4 cm^6 Sr^{-1}
\]

scattering volume V in number of unit cells can be considered as one big molecule.

\ce{CaF2} a material suitable for scattering efficiency S comparison measurement due to its large band gap ($S\times \omega_L^4$ is constant below 5eV).

symmetry-breaking mechanism,

\cite{Ahlgren2011}  low energy ion doping of graphene.

\section{misc}

\cite{Habib2010} oxygen plasma treatment on HF-etched Si (001). reaction among $e$, \ce{O^+}, \ce{O2^+}, \ce{O^-},\ce{O2}. \ce{OH}-terminated surface obtained.

\cite{Wang2014a} MB is a heterocyclic aromatic dye which is blue colored in oxidizing environment. Upon reduction, MB is turned into colorless leuco MB. This can be used as an oxygen indicator in food industry. Photo-bleaching of MB can be also due to its leuco formation rather than total decomposition. Photocatalytic decomposition can be minimized by keeping the solution at acidic condition (PH = 4), which will limit the formation of oxidative hydroxyl radicals (E = 2.8eV vs normal hydrogen electrode). Oxygen dissolved in the solution play a key role in conversion of LMB to MB under visible light. Purging with \ce{N2} for 20mins can remove dissolved oxygen.

@@

experience an enormous development, principles underlying, scarce. heavily engaged, extensively used, become aware of, a great deal of, consistently used, lift the restriction, changed profoundly, denominator, a situation which often arises as ... in a manner similar to its counterpart.

in reciprocal space, primitive cell, a sketch of device, a decisive role. anchors,angular brackets, thermodynamical average over the equilibrium configuration at temperature T.

equation embodies the law of conservation

become varied, laptop not hammer it hand, bubble pop, crash and burns.

### 2014-02-23 ch-tms/Seeded_growth_draft.tex
core-shell paper

To perform TEM-Raman integrated study, the core-shell nanowires need to be transferred to TEM grid first. So the core-shell specimens were dispersed into acetone, and then dipped onto polydimethylsiloxane (PDMS) substrate. Some long core-shell nanowires on PDMS substrate were picked up and transferred to TEM grids by using a home-built micromanipulator under optical microscope

@@

%fig TEM showing CS planes
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_coreshell_tem.jpg}
\caption{HRTEM images on one core-shell nanowires showing (a) the multilayer capping and void formation in \ce{WO_x} core, and (b) uniform \ce{WS2} layers on nanowire body and CS planes formation in core region.}
\label{fig:ws2tem}
\end{figure}
% fig Raman TEM
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_coreshell_integ.jpg}
\caption{TEM-Raman integrated results on one core-shell nanowires. (a)-(c) \ce{WS2} layer number variation from bulk to 2L. (d) Associated Raman spectra with site1-3 corresponding to HRTEM images (a)-(c), respectively. (e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensiteis ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.}
\label{fig:ws2ram}
\end{figure}

>>>>

To perform TEM-Raman integrated study, the core-shell nanowires need to be transferred to TEM grid first. So the core-shell specimens were dispersed into acetone, and then dipped onto polydimethylsiloxane (PDMS) substrate. Some long core-shell nanowires on PDMS substrate were picked up and transferred to TEM grids by using a home-built micromanipulator under optical microscope.

$6\mu L$ Methylene Blue\footnote{\ce{C16H18N3SCl} molar mass 319.85g/mol.} (Alfa Aesar 42771, 1\%w/v = 31.26 mM) in diluted into 20 mL DI water, giving ultimate concentration as $9.38 \mu M$. The measured absorbance spectrum is shown in supporting information, with maximum absorbance 0.42 at 664nm. Taking the \ce{MB^+} molar extinction coefficient $\epsilon$ as 95000 $M^{-1}cm^{-1}$,\cite{Cenens1988} then the measured concentration is $c = \frac{A}{\epsilon l}$ is $4.37 \mu M$.

@@

%fig TEM showing CS planes
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_coreshell_tem.jpg}
\caption{HRTEM images on one core-shell nanowires showing (a) the multilayer capping and void formation in \ce{WO_x} core, and (b) uniform \ce{WS2} layers on nanowire body and CS planes formation in core region.}
\label{fig:ws2tem}
\end{figure}
% fig Raman TEM
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_coreshell_integ.jpg}
\caption{TEM-Raman integrated results on one core-shell nanowires. (a)-(c) \ce{WS2} layer number variation from bulk to 2L. (d) Associated Raman spectra with site1-3 corresponding to HRTEM images (a)-(c), respectively. (e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensities ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.}
\label{fig:ws2ram}
\end{figure}
